Phenotypic evolution is more constrained in simpler food webs

### 2019-01-11 manuscript.Rmd
turns out my custom template is not needed, only the in_header document. This is because I manually specified the title page. If I wanted it produced in a similar format within YAML, I could keep my template.

---
# Decided to manually format the title page because I had greater control. Note that you should use put this info in the YAML header for compatability across document formats (e.g. html)
#title: Phenotypic evolution is more constrained in simpler food webs
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$ 
#- Christopher J. Greyson-Gaito$^{2,3}$ 
#- Arezoo Sootodeh$^{2}$ 
#- Brendan Locke$^{4}$ 
#- Jordi Bascompte$^{1}$ 
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    template: Rmd_AmNat_MS_template.tex
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

>>>>

---
# Decided to manually format the title page because I had greater control. Note that you should use put this info in the YAML header for compatability across document formats (e.g. html)
#title: Phenotypic evolution is more constrained in simpler food webs
#author: 
#- Matthew A. Barbour$^{1,2,\ast}$ 
#- Christopher J. Greyson-Gaito$^{2,3}$ 
#- Arezoo Sootodeh$^{2}$ 
#- Brendan Locke$^{4}$ 
#- Jordi Bascompte$^{1}$ 
# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
#date: | 
#    | 1. Affiliation
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib
    #template: Rmd_AmNat_MS_template.tex
    includes:  
      in_header: Am-Nat-preamble-latex.tex
bibliography: references
biblio-style: amnat
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---
